% 使用自定义类
\documentclass{sysureport}

% 可在文档中重新定义标题、作者等信息
\author{硕士}
% \title{可自定义标题} % 如需修改默认标题

\begin{document}

\maketitlepage

% 文档内容
\section{引言}
这是课程大作业的示例内容。

\section{理论分析}
使用自定义命令示例：\emphr{红色强调文本} 和 \emphg{绿色强调文本}。

% 数学公式示例
\begin{equation}
\dot{x} = Ax + Bu
\end{equation}

\section{Matlab 代码}

matlab代码高亮\url{https://ww2.mathworks.cn/matlabcentral/fileexchange/8015-m-code-latex-package}提供。


1) This inline demo \mcode{for i=1:3, disp('cool'); end;} uses the \verb|\mcode{}| command.\footnote{Works also in footnotes: \mcodefn{for i=1:3, disp('cool'); end;}}

2) The following is a block using the \verb|lstlisting| environment.
\begin{lstlisting}
for i = 1:3
	if i >= 5 && a ~= b       % literate programming replacement
		disp('cool');           % comment with some §\mcommentfont\LaTeX in it: $\mcommentfont\pi x^2$§
	end
	[:,ind] = max(vec);
	x_last = x(1,end) - 1;
	v(end);
	really really long really really long really really long really really long really really long line % blaaaaaaaa
	ylabel('Voltage (µV)');
end
\end{lstlisting}
Note: Here, the package was loaded with the \verb|framed|, \verb|numbered|, \verb|autolinebreaks| and \verb|useliterate| options.  \textbf{Please see the top of mcode.sty for a detailed explanation of these options.}


3) Finally, you can also directly include an external m-file from somewhere on your hard drive (the very code you use in \textsc{Matlab}, if you want) using the \verb|\lstinputlisting{/SOME/PATH/FILENAME.M}| command.  If you only want to include certain lines from that file (for instance to skip a header), you can use \verb|\lstinputlisting[firstline=6, lastline=15]{/SOME/PATH/FILENAME.M}|.

\subsection{FAQ}

\begin{description}
	\item[Why does {\tt delta} get replaced by $\Delta$, {\fontfamily{ptm}\selectfont\texttildelow=} by $\neq$, etc.?]
		Well, that's precisely what the \verb|useliterate| option does. If you don't want that, don't use it.
	\item[Can I get contiguous line numbers from one code block to another?]
		Yes, but you have to read the \verb|listings| documentation for that (Section~4.8 in particular).
	\item[{\tt mcode.sty} doesn't work in my document!] Well, try your (Matlab) code fragment in this demo document here to see whether there's something in it that might be causing a problem (not so likely, but possible), or if there's some conflict between the \verb|listings| package and some other package you have loaded.
	\item[Is feature XYZ possible?] Well, the \verb|listings| package might already be able to do that. Please consult its documentation (see red box at the top)!
\end{description}


% 参考文献
\begin{thebibliography}{99}
\bibitem{吴森堂} 吴森堂. 飞行控制系统[M]. 北京航空航天大学出版社, 2013.
\end{thebibliography}

\end{document}